\section{Fireball Whiskey Caramel Sauce}\index{desserts!fireball caramel sauce}

\begin{center}
Total Time: 50 minutes

\vspace{1em}

Source: http://www.siftingfocus.com/2013/02/vanilla-floats-with-fireball-whiskey-caramel-sauce-baking-recipe/

\end{center}

\subsection{Ingredients}
\begin{itemize}
    \item 1 1/2 cups granulated sugar
    \item 3 tablespoons corn syrup
    \item 1/2 cup heavy cream, warmed in the microwave for 30 seconds
    \item 2 tablespoons butter
    \item 1 teaspoon vanilla extract
    \item 1/2 cup Fireball Whiskey *
\end{itemize}

\subsection{Preparation}
\begin{enumerate}
    \item In a medium, heavy bottom skillet or saucepan, cook the sugar and
          corn syrup over medium heat, stirring occasionally, until the sugar
          has melted and turned a deep amber.
    \item Remove from the heat and carefully add the cream and butter.
    \item Return to the heat and stir until combined and smooth.
    \item Allow to cool for 30 minutes.
    \item Add the whiskey to the sauce and stir until completely combined.
    \item Use immediately, or store in an airtight container in the refrigerator for up to 3 weeks.  The caramel will firm up when chilled and must be re-warmed before using.
\end{enumerate}

* Caramel lends itself to so many different flavors.  If whiskey isn't
  your thing, try a liquor or brandy.  Or, you can substitute 1 tablespoon
  of vanilla extract for the whiskey.

FORMAT LATER
VANILLA ICE CREAM FLOATS WITH FIREBALL WHISKEY CARAMEL SAUCE

Vanilla ice cream
Vanilla soda
Fireball Whiskey Caramel Sauce
Whipped cream
Chocolate shavings or sprinkles
Red Hot candies
Place two scoops of ice cream into a tall glass.  Add vanilla soda to the glass and pour the whiskey sauce overtop.  Add a generous dollop of whipped cream and a sprinkling of chocolate and Red Hots.
