\section{Hershey's Chocolate Cake}\index{desserts!cake!Hershey's chocolate}

\begin{center}
Prep Time: 15 min |
Cook Time: 35 min |
Total Time: 60 min

\noindent Yield: 12 servings

\vspace{1em}

Source: https://www.hersheys.com/recipes/en-us/recipes/cakes-cupcakes/184/hersheys-perfectly-chocolate-chocolate-cake
\end{center}

\subsection{Ingredients}
\begin{multicols}{2}
\begin{itemize}
    \item 2 cups sugar
    \item 1-3/4 cups all-purpose flour
    \item 3/4 cup HERSHEY'S Cocoa
    \item 1-1/2 teaspoons baking powder
    \item 1-1/2 teaspoons baking soda
    \item 1 teaspoon salt
    \item 2 eggs
    \item 1 cup milk
    \item 1/2 cup vegetable oil
    \item 2 teaspoons vanilla extract
    \item 1 cup boiling water
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
    \item Heat oven to 350F. Grease and flour two 9-inch round baking pans.
    \item Stir together sugar, flour, cocoa, baking powder, baking soda and salt in large bowl. Add eggs, milk, oil and vanilla; beat on medium speed of mixer 2 minutes. Stir in boiling water (batter will be thin). Pour batter into prepared pans.
    \item Bake 30 to 35 minutes or until wooden pick inserted in center comes out clean. Cool 10 minutes; remove from pans to wire racks. Cool completely. Frost with preferred icing.
\end{enumerate}

\subsection{Variations}
\begin{description}
    \item[One-Pan Cake] \hfill \\
        Grease and flour 13x9x2-inch baking pan. Heat oven to 350F. Pour batter into prepared pan. Bake 35 to 40 minutes. Cool completely. Frost.
    \item[Three Layer Cake]  \hfill \\
        Grease and flour three 8-inch round baking pans. Heat oven to 350F. Pour batter into prepared pans. Bake 30 to 35 minutes. Cool 10 minutes; remove from pans to wire racks. Cool completely. Frost.
    \item[Bundt Cake]  \hfill \\
        Grease and flour 12-cup fluted tube pan. Heat oven to 350F. Pour batter into prepared pan. Bake 50 to 55 minutes. Cool 15 minutes; remove from pan to wire rack. Cool completely. Frost.
    \item[Cupcakes]  \hfill \\
        Line muffin cups (2-1/2 inches in diameter) with paper bake cups. Heat oven to 350F. Fill cups 2/3 full with batter. Bake 22 to 25 minutes. Cool completely. Frost. About 30 cupcakes.
\end{description}
