\section{Baked Ziti and Summer Veggies}\index{pasta!ziti!summer veggies}

\begin{center}
\noindent Total Time: 40 minutes

Yield: 4 Servings (1 1/2 cups each)

\vspace{1em}

Source: www.myrecipes.com/recipe/baked-ziti-summer-veggies-50400000113735/
\end{center}

\subsection{Ingredients}
\begin{multicols}{2}
\begin{itemize}
    \item 4 ounces uncooked ziti
    \item 1 tablespoon olive oil
    \item 2 cups chopped yellow squash
    \item 1 cup chopped zucchini
    \item 1/2 cup chopped onion
    \item 2 cups chopped tomato
    \item 2 garlic cloves, minced
    \item 1 cup (4 ounces) shredded part-skim mozzarella cheese, divided
    \item 2 tablespoons chopped fresh basil
    \item 2 teaspoons chopped fresh oregano
    \item 3/4 teaspoon salt, divided
    \item 1/8 teaspoon crushed red pepper
    \item 1/4 cup (2 ounces) part-skim ricotta cheese
    \item 1 large egg, lightly beaten
    \item Cooking spray
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
    \item Cook pasta according to package directions, omitting salt and fat; drain.
    \item Preheat oven to 400$^o$F.
    \item Heat a large skillet over medium-high heat. Add oil to pan. Add squash, zucchini, and onion; saut\'{e} 5 minutes. Add tomato and garlic; saut\'{e} 3 minutes. Remove from heat; stir in pasta, 1/2 cup mozzarella, herbs, 1/2 teaspoon salt, and pepper.
    \item Combine ricotta, remaining salt, and egg. Stir into pasta mixture. Spoon into an 8-inch square glass or ceramic baking dish coated with cooking spray; sprinkle with remaining mozzarella. Bake at 400° for 15 minutes or until bubbly and browned.
\end{enumerate}

\begin{table}%[H]
    \centering
    \begin{tabular}{|ll|c|}
        \hline
        Calories & & 301\\
        \hline
        Total Fat & & 12.1 g \\
        & Saturated Fat & 5.3 g\\
        & Mono-unsaturated Fat & 5.0 g\\
        & Poly-unsaturated Fat & 0.9 g\\
        \hline
        Protein & & 16 g\\
        \hline
        Total Carbohydrates & & 32.8 g\\
        & Fiber & 4.1 g\\
        \hline
        Cholesterol & & 65 g\\
        \hline
        Iron & & 1.9 mg\\
        \hline
        Sodium & & 640 mg\\
        \hline
        Calcium & & 291 mg\\
        \hline
    \end{tabular}
    \caption{Nutrition Information for Baked Ziti and Summer Veggies}
\end{table}
