\section{The Best Macaroni and Cheese Recipe Ever}\index{cheese!mac and}

Source: Kitchen Treaty

\begin{center}
Prep. Time: 30 minutes |
Total Time: 55 minutes | 
Yield: 5-6 servings
\end{center}

\subsubsection{Description}
The best macaroni and cheese recipe ever. Seriously. Creamy, cheesy, straightforward, ooey, gooey - this macaroni and cheese will knock your socks off.

\subsection{Ingredients}
\begin{multicols}{2}
\begin{itemize}
    \item 8 oz. (1/2 pound or about 1 3/4 cups) macaroni or other medium tubular pasta (like penne or conchiglie)*
    \item 3 tablespoons butter
    \item 1/4 cup flour
    \item 1/2 teaspoon salt
    \item 1/2 teaspoon dry mustard
    \item 1/4 teaspoon black pepper
    \item 1/8 teaspoon smoked paprika plus more for sprinkling on top
    \item 2 1/2 cups 2\% milk
    \item 3 cups grated medium cheddar cheese**
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
    \item Boil the pasta until al dente, according to package directions. Drain and rinse with cool water to stop the cooking, and return to the pan you boiled it in. Set aside. (Mix in a little butter to keep the noodles from sticking if it’s going to be awhile before you make the sauce)
    \item Preheat the oven to 375 degrees.
    \item Over medium heat, melt the butter.
    \item Add the flour, salt, dry mustard, pepper, and $\frac{1}{8}$ teaspoon smoked paprika. Stir constantly over medium heat for about three minutes.
    \item Stir in the milk.
    \item Keeping on medium heat, whisk constantly for about 10 minutes, until the sauce thickens.
    \item Remove from heat, and stir in 2 cups of the cheese, stirring until melted.
    \item Pour the cheese sauce over the noodles and toss gently until all noodles are covered.
    \item Add half the noodles to a two quart casserole dish.
    \item Sprinkle on half the cheese.
    \item Add the rest of the noodles.
    \item Sprinkle on the rest of the cheese, and dust lightly with the smoked paprika.
    \item Bake for about 25-30 minutes, until it starts getting a slightly dry and a tiny bit brown on top. Serve, topping individual servings with cooked, chopped bacon if desired.
\end{enumerate}
 
\subsubsection{Notes}
Adapted from the Bev’s Macaroni and Cheese recipe on Food.com 

\noindent * Please resist the urge to add more noodles to stretch the recipe. You need a lot of sauce with that pasta because the pasta soaks so much and it otherwise cooks down. Over-dry mac and cheese is such a disappointment – don't do it! 

\noindent ** Also resist the urge to add more cheese to the sauce. This can do weird things. Sprinkle more in between and on top if you must have more cheese.
