\section{Chicken Florentine Pasta}\index{pasta!chicken florentine}\index{poultry!chicken!florentine pasta}

\begin{center}
Prep. Time: 10 minutes |
Cook Time: 20 minutes|
Total Time: 30 minutes
 
Yield: 10 servings

\vspace{1em}

Source: Ree Drummond\par
http://thepioneerwoman.com/cooking/2012/04/chicken-florentine-pasta/
\end{center}

\subsection{Ingredients}
\begin{itemize}
    \item 1 pound Penne
    \item 4 whole Boneless, Skinless Chicken Breasts
    \item Salt And Pepper, to taste
    \item 2 Tablespoons Butter
    \item 2 Tablespoons Olive Oil
    \item 4 cloves Garlic, Minced
    \item 3/4 cups Dry White Wine
    \item 3/4 cups Low-sodium Broth, More If Needed
    \item 1 bag Baby Spinach
    \item 2 cups Grape Tomatoes, Halved Lengthwise
    \item 4 ounces, weight Parmesan Cheese, Shaved With Vegetable Peeler
\end{itemize}

\subsection{Preparation}
\begin{enumerate}
    \item Cook pasta according to package directions in lightly salted water. Drain and set aside.
    \item Cut chicken breasts into chunks and sprinkle on salt and pepper.
    \item Heat butter and olive oil over high heat in a large skillet. Add chicken chunks in a single layer and do not stir for a minute or two in order to allow the chicken to brown on the first side. Turn the chicken and brown on the other side. Cook until done, then remove chicken from the skillet.
    \item Turn heat to medium. Add garlic and quickly stir to avoid burning. After about 30 seconds, pour in wine and broth, stirring to deglaze the pan. Allow the liquid to bubble up, then continue cooking until it's reduced by at least half (most of the surface of the liquid should be bubbling at this point.)
    \item Turn off the heat. Add spinach, tomatoes, chicken, and cooked pasta to the skillet. Toss to combine; the spinach will wilt as you toss everything. Add plenty of Parmesan shavings and toss to combine.
    \item Serve with extra Parmesan shavings.

\end{enumerate}
