\section{Farro and Herb Pilaf with Sausage, Mushrooms and Spinach}\index{grains!farro!herb pilaf with sausage, mushrooms, and spinach}

\begin{center}
Prep Time: 10 min | 
Cook Time: 45 min |
Total Time: 55 min

\noindent Yield: 4 servings

\vspace{1em}

Source: http://www.wholefoodsmarket.com/recipe/farro-and-herb-pilaf-sausage-mushrooms-and-spinach
\end{center}

\subsection{Ingredients}
\begin{multicols}{2}
\begin{itemize}
    \item 1 1/2 tablespoon extra-virgin olive oil, divided
    \item 1 1/2 cup farro
    \item 3 1/2 cup low-sodium chicken broth
    \item 3 links mild or sweet Italian pork sausage, removed from casings
    \item 1 cup chopped red onion
    \item 2 cloves garlic, finely chopped
    \item 2 cups cremini or button mushrooms, halved or quartered
    \item 2 cups packed baby spinach
    \item Salt and pepper to taste
    \item 1/4 cup chopped parsley
    \item 2 tablespoons chopped oregano
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
    \item Heat 1 tablespoon of the oil in a medium pot over medium-high heat. Add farro and cook, stirring often, until fragrant and toasted, 4 to 5 minutes. Add broth and bring to a boil. Reduce heat to medium, cover and cook, stirring occasionally, until liquid is absorbed and farro is tender, 20 to 25 minutes. 
    \item Meanwhile, heat remaining 1/2 tablespoon oil in a large skillet over medium-high heat. Add sausage and cook, breaking it up into small chunks with a spatula, until almost cooked through, 6 to 8 minutes. Add onions and garlic and cook until onions are translucent, about 5 minutes. Add mushrooms, toss well and cook, stirring occasionally, until just softened, 4 to 5 minutes. Remove skillet from the heat and stir in spinach until wilted. Season with salt and pepper.
    \item Stir parsley, oregano, salt and pepper into pot with farro, then spoon onto plates. Top with sausage-mushroom mixture and serve.
\end{enumerate}

Per Serving: Serving size: , 490 calories (190 from fat), 22g total fat, 6g saturated fat, 35mg cholesterol, 910mg sodium, 57g carbohydrates, (9g dietary fiber, 8g sugar), 22g protein.
