\section{Farro Salad with Tomato , Cucumber \& Basil}\index{grains!farro!salad}

\begin{center}
\noindent Prep. Time: 10 minutes |
Total Time: 30 minutes | 
Yield: 5 Servings

\vspace{1em}

Source: http://www.thekitchn.com/recipe-summer-farro-salad-with-tomato-cucumber-amp-basil-recipes-from-the-kitchn-193060
\end{center}

\subsection{Ingredients}
\begin{multicols}{2}
\begin{itemize}
    \item Olive oil, for cooking
    \item 2 large shallots (or 1 sweet onion), finely chopped
    \item 2 cups farro (uncooked)
    \item 4 cups chicken or vegetable stock
    \item 1/4 cup red wine vinegar
    \item 2 tablespoons olive oil
    \item 1 pint cherry or grape tomatoes, halved or quartered
    \item 1/2 large English (hothouse) cucumber, diced
    \item 1/4 cup finely chopped basil
    \item Kosher salt and freshly ground black pepper
    \item 1 tablespoon Dijon mustard (optional)
\end{itemize}
\end{multicols}

\subsubsection{Possible Additions}
Crumbled feta or goat cheese; pickled shallots, red onions, or corn; chopped mint or dill.

\subsection{Preparation}
\begin{enumerate}
    \item Heat a few tablespoons olive oil in a heavy saucepan over medium heat. Add the shallots and saut\'{e} until translucent, about 5 minutes. Add the farro and cook, stirring to coat each grain, 1 to 2 minutes. 
    \item Pour in the stock and bring to a boil. Reduce heat to a simmer, cover, and cook until farro is soft but still chewy in the center, about 12 minutes. (If there is more than a tablespoon or two of leftover stock, strain it out.)
    \item Cool the farro to room temperature. Add the red wine vinegar and olive oil, and stir to combine. Fold in tomatoes, cucumbers, and basil. Season with salt and pepper, and adjust vinegar and oil amounts to taste. Serve chilled or at room temperature.
\end{enumerate}

