\section{Healthy Farro Stir-fry}\index{grains!farro!stir-fry}

\begin{center}
Prep Time: 15 min |
Cook Time: 25 min |
Total Time: 40 min

\noindent Yield: 4 servings

\vspace{1em}

Source: http://www.foodnetwork.com/recipes/food-network-kitchens/healthy-farro-fried-rice.html 
\end{center}

\subsection{Ingredients}
\begin{multicols}{2}
\begin{itemize}
 \item 1 cup farro
 \item 1 bunch scallions, sliced, white and green parts kept separate
 \item 2 cloves garlic, finely chopped
 \item 1 inch piece peeled fresh ginger, finely chopped
 \item Pinch crushed red pepper
 \item Kosher salt
 \item Pinch sugar
 \item 1 tablespoon plus 1 teaspoon vegetable oil
 \item 1 medium carrot, thinly sliced
 \item 1 cup thawed frozen peas
 \item 1 cup bean sprouts
 \item 2 tablespoons low-sodium soy sauce
 \item 1 teaspoon toasted sesame oil
 \item 2 large eggs, lightly beaten
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
    \item Bring a medium saucepan filled two-thirds full of water to a boil. Add the farro and cook until tender but still chewy, about 15 minutes. Drain well and cool. (This can be done one day ahead).
    \item Combine the scallion whites, garlic, ginger, crushed red pepper, 1/2 teaspoon salt and sugar in a small bowl and keep near the stove top.
    \item Heat 1 tablespoon of the oil in a large nonstick skillet or wok over medium-high heat. Add the carrot and cook, stirring constantly, until crisp-tender, about 2 minutes. Add the scallion white mixture and continue to stir fry until fragrant, about 30 seconds. Add the cooled farro, half the scallion greens, the peas, bean sprouts, soy sauce and sesame oil and stir fry until the farro is hot, about 2 minutes. Remove from the heat and transfer to a serving dish.
    \item Wipe out the skillet, add the remaining 1 teaspoon of oil and place over medium-high heat. Add the eggs and a large pinch of salt; let cook undisturbed until the eggs begin to bubble up, then stir constantly, breaking the eggs up into small pieces, until they are cooked through, about 30 seconds. Scrape eggs over the farro and stir to incorporate. Sprinkle with the remaining scallion green and serve hot.
\end{enumerate}

\begin{table}%[H]
    \centering
    \begin{tabular}{|ll|c|}
        \hline
        Calories & & 280\\
        \hline
        Fat & & 9 g\\
        \hline
         & Saturated & Fat 1.5 g\\
        \hline
        Carbohydrate & & 39 g\\
        \hline
         & Sugar & 6 g\\
         & Fiber & 7 g\\
        \hline
        Protein & & 12 g\\
        \hline
        Cholesterol & & 95 mg\\
        \hline
        Sodium & & 580 mg\\
        \hline
    \end{tabular}
    \caption{Nutrition Information for healthy farro stir-fry}
\end{table}
