\section{Homemade Pepperoni Pizza Pockets (Copycat Hot Pockets)}\index{pizza!homemade pepperoni pizza pockets}

\begin{center}
Prep Time: 20 min |
Cook Time: 20 min |
Total Time: 40 min

\noindent Yield: 6 pizza pockets

\vspace{1em}

    Source: Rachel Singer (\url{https://www.mashupmom.com/homemade-pepperoni-pizza-pockets-copycat-hot-pockets/})
\end{center}

\subsection{Ingredients for the Sauce}
\begin{multicols}{2}
\begin{itemize}
  \item 8 oz can tomato sauce
  \item 6 oz can tomato paste
  \item 1 tsp olive oil
  \item 1 tsp minced garlic about 2 cloves
  \item 2 tsp Italian seasoning
  \item 1 tsp oregano
  \item 1/2 tsp sugar
  \item 1/4 tsp crushed red pepper
  \item Sea salt to taste
\end{itemize}
\end{multicols}

\subsection{Ingredients for the Pockets}
\begin{multicols}{2}
\begin{itemize}
  \item 4 oz pepperoni slices cut into quarters
  \item 4 oz shredded mozzarella 1 cup
  \item 1 box refrigerated pie crust both crusts
  \item 1 Tbsp butter melted
  \item 2 Tbsp shredded Parmesan
  \item 1/2 tsp parsley
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
  \item Preheat the oven to 400 degrees and remove pie crust from the refrigerator to soften as directed on the box. Spray a rimmed baking sheet with cooking spray.
  \item Add all of the sauce ingredients to a medium sized mixing bowl. Stir to combine.
  \item Cut the pepperoni into quarters, and shred the mozzarella if not using pre-shredded. Combine pepperoni, mozzarella, and 1/2 cup of the sauce in a large bowl.
  \item Unroll the pie crusts and cut each crust into three equal wedges, so that you have six pieces total. Spoon equal amounts of the filling into one side of each of the pie crust wedges.
  \item Fold each wedge in half over the filling, then crimp the edges together. Arrange pizza pockets in a single layer on the prepared baking sheet.
  \item Melt butter in the microwave. Brush each pizza pocket lightly with butter, then top each with Parmesan and parsley. 
  \item Bake for 20 minutes at 400 degrees, or until pizza pockets are golden brown. Serve with the remaining pizza sauce for dipping.
\end{enumerate}
