\section{Quinoa and Vegetable Stuffed Peppers}\index{grains!quinoa!stuffed peppers with vegetables}

\begin{center}
Prep Time: 25 min |
Cook Time: 45 min |
Total Time: 70 min

\noindent Yield: 6 servings

\vspace{1em}

Source: http://www.foodnetwork.com/recipes/rachael-ray/quinoa-and-vegetable-stuffed-peppers-recipe.html
\end{center}

\subsection{Ingredients}
\begin{multicols}{2}
\begin{itemize}
    \item 1 cup quinoa
    \item 2 cups chicken or vegetable stock
    \item 6 small bell peppers, mixed colors, seeded and halved
    \item 3 tablespoons EVOO, plus extra for drizzling
    \item Salt and freshly ground black pepper
    \item 4 cloves garlic, thinly sliced
    \item 1 small firm eggplant, trimmed of half the skin, chopped
    \item 1 small to medium firm zucchini, seeded and chopped
    \item 1 red onion, chopped
    \item 1 fresh chile pepper, such as Fresno, thinly sliced, or 1 teaspoon dried crushed pepper
    \item 1/2 cup fresh flat-leaf parsley leaves, chopped
    \item 1/4 cup fresh mint leaves, a handful, chopped
    \item 2 plum tomatoes, chopped
    \item 1 cup crumbled feta or ricotta salata cheese
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
    \item Preheat the oven to 450 degrees F.
    \item Bring the quinoa and stock to a boil. Cover and simmer until the liquid is absorbed and the grain looks translucent, 12 to 15 minutes. Then fluff with a fork. You will have about 4 cups of cooked grain.
    \item Drizzle the bell pepper halves with EVOO and season both sides with salt and pepper. Roast cut-side down until the skins begin to char and the peppers are just tender, about 20 minutes. Remove from the oven and cool to room temp, then arrange in a baking dish cut-side up.
    \item Meanwhile, heat 3 tablespoons EVOO, 3 turns of the pan, over medium-high heat. Add the garlic, eggplant, zucchini, onions and chiles, and season with salt and pepper. Cook partially covered to tender, 10 to 12 minutes. Add the herbs and tomatoes, and combine with the quinoa.
    \item Fill the pepper halves with the quinoa and vegetable stuffing and drizzle with EVOO. Cool and chill for a make-ahead meal. To serve, roast in a 375 degree F oven until the peppers are hot through. Serve the pepper halves topped with lots of cheese crumbles.
\end{enumerate}
