\section{Quinoa Vegetable Salad}\index{grains!quinoa!quinoa vegetable salad}

\begin{center}
Prep Time : 20 minutes |
Cook Time : 25 minutes |
\noindent Total Time: 90 minutes

\noindent Yield: 5 cups

\vspace{1em}

Source: http://allrecipes.com/recipe/quinoa-vegetable-salad
\end{center}

\subsection{Ingredients}
\begin{multicols}{2}
\begin{itemize}
    \item 1 teaspoon canola oil
    \item 1 tablespoon minced garlic
    \item 1/4 cup diced (yellow or purple) onion
    \item 2 1/2 cups water
    \item 2 teaspoons salt, or to taste
    \item 1/4 teaspoon ground black pepper
    \item 2 cups quinoa
    \item 3/4 cup diced fresh tomato
    \item 3/4 cup diced carrots
    \item 1/2 cup diced yellow bell pepper
    \item 1/2 cup diced cucumber
    \item 1/2 cup frozen corn kernels, thawed
    \item 1/4 cup diced red onion
    \item 1 1/2 tablespoons chopped fresh cilantro
    \item 1 tablespoon chopped fresh mint
    \item 1 teaspoon salt
    \item 1/4 teaspoon ground black pepper
    \item 2 tablespoons olive oil
    \item 3 tablespoons balsamic vinegar
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
    \item Heat the canola oil in a saucepan over medium heat.
    \item Cook and stir the garlic and 1/4 cup onion in the hot oil until the onion has softened and turned translucent, about 5 minutes.
    \item Pour in the water, 2 teaspoons salt, and 1/4 teaspoon black pepper and bring to a boil; stir the quinoa into the mixture, reduce heat to medium-low, and cover. Simmer until the quinoa is tender, about 20 minutes.
    \item Drain any remaining water from the quinoa with a mesh strainer and transfer to a large mixing bowl. Refrigerate until cold.
    \item Stir the tomato, carrots, bell pepper, cucumber, corn, and 1/4 cup red onion into the chilled quinoa. Season with cilantro, mint, 1 teaspoon salt, and 1/4 teaspoon black pepper. Drizzle the olive oil and balsamic vinegar over the salad; gently stir until evenly mixed.

\end{enumerate}
