\section{Southwestern Mac and Cheese}\index{cheese!mac and}

\begin{center}
Prep. Time: 15 minutes |
Total Time: 60 minutes | 
Yield: 10 servings
\end{center}

\subsubsection{Description}
Add some spice to everyone's favorite comfort food. This mac and cheese has a Southwestern accent from the Monterey Jack cheese, green chiles and Southwest Seasoning.

\subsection{Ingredients}
\begin{multicols}{2}
\begin{itemize}
    \item 1 pound pasta, such as medium shells or penne
    \item 1/4 cup (1/2 stick) butter
    \item 1/4 cup flour
    \item 1 tablespoon McCormick® Gourmet Collection Southwest Seasoning
    \item 1 1/2 teaspoons McCormick® Gourmet Collection Mustard, Ground
    \item 5 cups milk
    \item 1 1/2 cups shredded Cheddar cheese
    \item 1 1/2 cups shredded Monterey Jack cheese
    \item 1/4 cup grated Parmesan cheese
    \item 1 pint grape tomatoes, halved
    \item 1 can (4 1/2 ounces) chopped green chiles
    \item 1 1/2 cups panko (Japanese bread crumbs)
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
    \item Preheat oven to 350°F. Cook pasta in large saucepan as directed on package for al dente pasta. Rinse under cold water; drain well.
    \item Melt butter in same saucepan on medium heat. Sprinkle with flour and spices. Cook and stir 2 minute or until well blended. Gradually stir in milk until smooth. Stirring constantly, cook 3 minutes or until sauce starts to thicken. Stir in cheeses until melted and smooth. Remove from heat. Add pasta, tomatoes and chiles; toss gently to coat. Pour into greased 13x9-inch baking dish. Sprinkle panko evenly over top.
    \item Bake 30 minutes or until bubbly and golden brown on top. Let stand 5 minutes before serving.
\end{enumerate}

\subsubsection{Nutrition Info}
Calories: 467

\noindent Fat: 19 g

\noindent Carbohydrates: 53 g

\noindent Cholesterol: 55 mg

\noindent Sodium: 422 mg

\noindent Fiber: 3 g

\noindent Protein: 21 g
