\section{Tuscan Butter Gnocchi}\index{pasta!tuscan butter gnocchi}

\begin{center}
Prep Time: 10 min |
Cook Time: 35 min |
Total Time: 45 min

\noindent Yield: 8 servings

\vspace{1em}

    Source: Makinze Gore (\url{https://www.delish.com/cooking/recipe-ideas/a22845363/tuscan-butter-gnocchi-recipe/})
\end{center}

\subsection{Ingredients}
\begin{multicols}{2}
\begin{itemize}
  \item 4 tbsp. butter
  \item 3 cloves garlic, minced
  \item 2 c. halved cherry tomatoes 
  \item 1 tsp. dried oregano 
  \item Kosher salt 
  \item Freshly ground black pepper
  \item Pinch red pepper flakes 
  \item 4 c. baby spinach 
  \item 1 c. low-sodium chicken broth
  \item 1 c. heavy cream 
  \item 1/2 c. freshly grated Parmesan 
  \item 1/4 c. freshly chopped herbs (such as basil and parsley), plus more for garnish 
  \item 2 (17.5-oz.) packages gnocchi
  \item 1 c. shredded mozzarella
  \item Lemon wedges, for serving
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
  \item Preheat oven to 350$^o$F. In a large skillet over medium heat, melt butter. Add garlic and cook until fragrant, 1 minute. Add cherry tomatoes and season with oregano, salt, pepper, and a pinch of red pepper flakes. Cook until tomatoes are beginning to burst then add spinach and cook until beginning to wilt.
  \item Stir in broth, heavy cream, Parmesan, and herbs and bring to a simmer. Reduce heat to low and simmer until sauce is slightly reduced, about 3 minutes. 
  \item Add gnocchi and toss to coat. Pour gnocchi into a 9''-x-13'' baking pan and top with mozzarella. Bake until gnocchi is cooked through and cheese is melty, 30 minutes. 
  \item Garnish with more herbs and squeeze lemon on top before serving.
\end{enumerate}
