\section{The Best Chili You Will Ever Taste}\index{chili}

Prep. Time: 30 minutes |
Total Time: 2 hours 30 minutes | 
Yield: 6-8 servings

\subsubsection{About This Recipe}

``This is the best chili recipe I have ever tried. I'm not sure where the recipe
originated, but it is amazing! Sometimes, I don't bother adding all four cans
of the kidney beans and it still turns out wonderful. Once anyone tastes this
chili, they will be begging for the recipe!! Enjoy!''

\subsection{Ingredients}
\begin{multicols}{2}
\begin{itemize}
    \item 2 teaspoons oil
    \item 2 onions, chopped
    \item 3 cloves garlic, minced
    \item 1 lb lean ground beef
    \item 3/4 lb beef sirloin, cubed
    \item 1 (14 1/2 ounce) cans diced tomatoes
    \item 1 can dark beer
    \item 1 cup strong coffee
    \item 2 (6 ounce) cans tomato paste
    \item 1 can beef broth
    \item 1/2 cup brown sugar
    \item 3 1/2 tablespoons chili sauce
    \item 1 tablespoon cumin
    \item 1 tablespoon cocoa
    \item 1 teaspoon oregano
    \item 1 teaspoon cayenne
    \item 1 teaspoon coriander
    \item 1 teaspoon salt
    \item 4 (15 ounce) cans kidney beans
    \item 4 chili peppers, chopped
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
    \item Heat oil.
    \item Cook onions, garlic and meat until brown.
    \item Add tomatoes, beer, coffee, tomato paste and beef broth.
    \item Add spices Stir in 2 cans of kidney beans and peppers.
    \item Reduce heat and simmer for 1 1/2 hours.
    \item Add 2 remaining cans of kidney beans and simmer for another 30 minutes.
\end{enumerate}
