\section{Onion and Pepper Round Steak}\index{meat!steak!round}

Prep. Time: 15 minutes |
Total Time: 1 hour 30 minutes 

\noindent Source: Emeril Lagasse (http://www.foodnetwork.com/recipes/emeril-lagasse/onion-and-pepper-smothered-round-steak-recipe/index.html)

\subsection{Ingredients}
\begin{itemize}
    \item 2 1/4 pounds thin top round steak, sliced into strips about 1/4-inch thick
    \item 1 1/2 tablespoons Essence, recipe follows
    \item 1/4 cup vegetable oil
    \item 3 tablespoons all-purpose flour
    \item 3 cups chicken broth, divided
\end{itemize}

\subsection{Preparation}
\begin{enumerate}
    \item Combine the meat with the Essence and flour in a mixing bowl and toss to combine.
    \item Heat the oil in a large cast iron Dutch oven or high-sided skillet over medium-high heat and brown the meat, in batches, until browned on all sides, 4 to 5 minutes.
    \item Add 2 cups of the chicken broth and stir, scraping the bottom and sides of the pan to loosen any browned particles.
    \item Add the onions, bell peppers, salt, cayenne, and black pepper. Cook, stirring frequently, for 6 to 8 minutes, or until the vegetables are wilted.
    \item Reduce the heat to medium. Cover and cook, stirring occasionally, for 15 minutes.
    \item Add the remaining cup of broth and continue to cook, uncovered, for about 1 hour longer, or until the meat is very tender and the gravy is thickened and flavorful.
    \item Add the parsley and serve immediately over white rice, if using.
\end{enumerate}
