\section{Roasted Pork with Vegetables}\index{meat!pork!roasted pork with vegetables}

\begin{center}
Prep Time: 15 min |
Cook Time: 60 min |
Total Time: 75 min

\noindent Yield: 6 Servings

\vspace{1em}

    Source: Steve Cylka (\url{https://www.theblackpeppercorn.com/roasted-pork-tenderloin-with-vegetables/})
\end{center}

\subsection{Ingredients}
\begin{multicols}{2}
\begin{itemize}
    \item 2 pork tenderloins
    \item 2 medium onion , chopped
    \item 5 medium carrots , peeled and chopped
    \item 4 medium potatoes , chopped
    \item 2 asian eggplant (or 1 standard eggplant) , chopped
    \item 10 mushrooms , halved
    \item 4 tbsp oil
    \item 6 cloves garlic , minced
    \item 1 tbsp salt
    \item 1 tbsp black pepper
    \item 1 tbsp oregano
    \item 2 tsp paprika
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
    \item Preheat oven to 400F.
    \item Spread roasted vegetables evenly across the bottom of a roasting pan. Drizzle oil all over the vegetables.
    \item Roast vegetables for 30-35 minutes or until the vegetables are just starting to get tender.
    \item Trim the pork tenderloin of any excess fat and membrane.
    \item Make the seasoning rub by mixing together the minced garlic, salt, black pepper, oregano and paprika. Rub all over the pork tenderloin.
    \item Move the vegetables in the middle to make room to place the pork tenderloin. Lay the pork tenderloin in the cleared out area, making sure that the pork tenderloin are not touching each other.
    \item Place back into the oven and roast until the pork tenderloin is cooked and reaches an internal temperature of 145F, about 25 minutes.
    \item If desired, garnish with minced fresh parsley.
    \item Serve.
\end{enumerate}

\subsection{Notes}
I subbed out the veggies listed here with zucchini, parsnips, carrots, onions, and mushrooms.

\subsection{Nutrition}
Per serving:

\begin{itemize}
    \item Calories: 440kcal
    \item Carbohydrates: 39g
    \item Protein: 43g
    \item Fat: 14g
    \item Saturated Fat: 2g
    \item Cholesterol: 109mg
    \item Sodium: 1309mg
    \item Fiber: 11g
    \item Sugar: 10g
\end{itemize}
