\section{Skillet Pork and Peppers}\index{meat!pork!skillet pork and peppers}

\begin{center}
Prep Time: 20 min |
Cook Time: 22 min |
Total Time: 42 min

\noindent Yield: 4 servings

\vspace{1em}

Source: http://www.foodnetwork.com/recipes/food-network-kitchens/skillet-pork-and-peppers-recipe.html
\end{center}

\subsection{Ingredients}
\begin{multicols}{2}
\begin{itemize}
    \item 1 large pork tenderloin (about 11/2 pounds), trimmed
    \item Kosher salt
    \item 3 tablespoons extra-virgin olive oil
    \item 1 small onion, thickly sliced
    \item 2 red and/or yellow bell peppers, sliced into wide strips
    \item 6 cloves garlic, smashed
    \item 16 fresh sage leaves
    \item 2 tablespoons tomato paste
    \item 1/4 cup sliced pickled pepperoncini, plus 2 teaspoons liquid from the jar
    \item 1/3 cup dry white wine
    \item 2/3 cup low-sodium chicken broth
    \item 1/4 cup grated parmesan cheese
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
    \item Preheat the broiler. Slice the pork on an angle into 1-inch-thick pieces; season with salt. Heat a large ovenproof skillet over medium-high heat; add 1 tablespoon olive oil. Add the onion and bell peppers; season with 1/2 teaspoon salt and cook until the vegetables are crisp-tender and slightly browned, 4 to 6 minutes. Transfer to a plate.
    \item Add the remaining 2 tablespoons oil to the skillet. Add the pork and sear over high heat until browned, 2 to 4 minutes per side. Transfer the pork to the plate with the onion and peppers.
    \item Reduce the heat to medium and add the garlic, sage and tomato paste to the skillet. Cook, stirring, until the tomato paste turns brick-red, about 1 minute. Add the pepperoncini slices and their liquid, then pour in the wine and bring to a boil. Add the broth and return to a simmer. Arrange the pork in a single layer in the skillet; add the onion and peppers and sprinkle with cheese. Transfer to the oven and broil until the pork is cooked through, 4 to 7 minutes.
\end{enumerate}

Per serving: Calories 380; Fat 18 g (Sat. 4.4 g; Mono. 10.5 g; Poly. 2 g); Cholesterol 115 mg; Sodium 586 mg; Carbohydrate 10 g; Fiber 2 g; Protein 40 g
