\section{Slow Cooker Pork}\index{meat!pork!slow cooker pork}\index{slow cooker!slow cooker pork}

\begin{center}
Prep Time: 15 min |
Cook Time: 7 hours |
Total Time: 7.25 hours

\noindent Yield: 6-8 servings

\vspace{1em}

Source: Geri McGill
\end{center}

\subsection{Ingredients}
\begin{multicols}{2}
\begin{itemize}
    \item 3 lb pork shoulder
    \item 6-8 green onions
    \item 4 cloves garlic, minced
    \item 1/2 cup brown sugar
    \item 1/2 cup white sugar
    \item 1 tsp paprika
    \item 1 tsp basil, dried
    \item 1 tsp black pepper
    \item 1/3 cup Worcestershire sauce
    \item 1/3 cup water
    \item 2 tbsp honey
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
    \item Spray the slow cooker with a light coating of non-stick spray.
    \item Chop the onions and place in the slow cooker.
    \item Cut off the skins of the garlic cloves and cut lengthwise into slivers. Put about 2 cloves worth into the bottom of the crock pot with the onions.
    \item With a small paring knife, cut slits all over the roast. Place a sliver of the remaining garlic into each of the slits.
    \item In a small bowl, mix the sugars and spices. Rub this all over the meat until it is covered. Place the roast into the slow cooker. Place any of the remaining spice mixture into the crock pot over the roast.
    \item In another small bowl, mix the water, Worcestershire sauce, and honey together. Pour the liquid mixture over the roast.
    \item Cook on high for about 7 hours. (optional) Mix with BBQ sauce for pulled pork sandwiches.
\end{enumerate}
