\section{Steakhouse Burgers}\index{meat!burgers!steakshoue burgers}

\begin{center}
Prep Time: 10 min
Cook Time: 10 min
Total Time: 20 min

\noindent Yield: 8

\vspace{1em}

    Source: \href{https://www.onceuponachef.com/recipes/steakhouse-burgers.html}{Jenn Segal}
\end{center}

\subsection{Ingredients}
\begin{multicols}{2}
\begin{itemize}
    \item 2 pieces white sandwich bread, crusts removed and cut into 1/4-inch pieces
    \item 1/3 cup low fat milk
    \item 2-1/2 teaspoons kosher salt
    \item 1 teaspoon freshly ground black pepper
    \item 3 garlic cloves, minced
    \item 1-1/2 tablespoons Worcestershire sauce
    \item 2 tablespoons ketchup
    \item 3 pounds 85\% lean ground beef
    \item 3 scallions, finely sliced (optional)
    \item Non-flammable cooking spray to grease grill
    \item 8 hamburger buns
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
    \item Preheat the grill to high heat.
    \item In a large bowl, mash the bread and milk together with a fork until it forms a chunky paste. Add the salt, pepper, garlic, Worcestershire sauce and ketchup and mix well.
    \item Add the ground beef and scallions and break the meat up with your hands. Gently mix everything together until just combined. Do not over-mix. Divide the mixture into 8 equal portions and form loose balls. Flatten the balls into 3/4-inch patties about 4-1/2 inches across. Form a slight depression in the center of each patty to prevent the burgers from puffing up on the grill.
    \item Grease the grill with non-flammable cooking spray. Grill the burgers, covered, until nicely browned on the first side, 2-4 minutes. Flip burgers and continue cooking for a few minutes more until desired doneness is reached. Before serving, toast the buns on the cooler side of the grill if desired.
    \item \textbf{Note}: The nutritional information doesn't include the hamburger buns
    \item \textbf{Freezer-Friendly Instructions}: The uncooked burgers can be frozen for up to three months. (Freeze the burgers on a baking sheet or plate so their shape sets, then transfer them to a sealable plastic bag for easy storage.) Defrost the burgers overnight in the refrigerator prior to serving and then cook as directed.
\end{enumerate}

\subsection{Nutrition Information}
\begin{itemize}
    \item Serving size:1 burger
    \item Calories:517
    \item Fat:27 g
    \item Saturated fat:10 g
    \item Carbohydrates:28 g
    \item Sugar:5 g
    \item Fiber:1 g
    \item Protein:37 g
    \item Sodium:567 mg
    \item Cholesterol:116 mg
\end{itemize}
