\section{Borlotti Beans in Tomato Sauce with Creamy Polenta}\index{veg!beans!borlotti beans in tomato sauce with creamy polenta}

\begin{center}
Prep Time: 10 min |
Cook Time: 60 min |
Total Time: 75 min

\noindent Yield: 4-6 servings

\vspace{1em}

Source: http://www.epicurious.com/recipes/food/views/red-beans-and-rice-1259
\end{center}

\subsection{Ingredients}
\begin{itemize}
    \item 2 cups drained, cooked borlotti beans (http://www.thekitchn.com/thekitchn/tips-techniques/how-to-cook-beans--043766)
    \item 1/3 cup chopped fresh flat-leaf parsley
\end{itemize}
Tomato Sauce
\begin{multicols}{2}
\begin{itemize}
    \item 3 tablespoons unsalted butter
    \item 1/2 medium yellow onion, chopped 
    \item 1 medium fennel bulb, trimmed and chopped 
    \item 3 garlic cloves, finely chopped
    \item 4 teaspoons chopped fresh oregano
    \item 1/4 teaspoon red pepper flakes
    \item Salt
    \item 1 small carrot, peeled and shredded
    \item One 28-ounce can whole San Marzano tomatoes or plum tomatoes
    \item Freshly ground pepper
\end{itemize}
\end{multicols}

Polenta
\begin{multicols}{2}
\begin{itemize}
    \item 4 cups water
    \item 1 teaspoon salt
    \item 1 cup polenta
    \item 2 tablespoons unsalted butter
    \item 1/2 cup freshly grated Parmesan cheese, plus more for garnishing
    \item Freshly ground pepper
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
    \item Make the sauce: In a small Dutch oven or other heavy pot over medium heat, melt the butter. Add the onion, the fennel, the garlic, 2 teaspoons of the oregano, the red pepper flakes, and a pinch of salt. Saut\'{e} until the vegetables are soft and fragrant, about 10 minutes. Add the carrot and saut\'{e} for 2 to 3 minutes. Add the tomatoes, stirring to break them up with a wooden spoon. Add another pinch of salt. Reduce the heat to low and cook, uncovered, at the barest simmer, stirring occasionally, until the tomatoes are reduced and beginning to separate from the oil, at least 2 hours or up to 3 hours. Add the remaining 2 teaspoons oregano and salt and pepper to taste. The sauce can be made up to this point 1 or 2 days ahead. Let cool and refrigerate.
    \item Make the polenta: About 45 minutes before serving, bring the water to a boil in a medium, heavy-bottomed saucepan. Add the salt and, whisking continuously, slowly pour the polenta into the water in a thin stream. Reduce the heat to low and cook, stirring nearly constantly with a long-handled wooden spoon, until the mixture thickens, the grains soften, and the polenta begins to pull away from the sides of the pan, 40 to 45 minutes. Stir in the butter and 1/2 cup of the Parmesan, and season with pepper. Cover to keep warm.
    \item Add the beans to the tomato sauce and warm them together over medium-low heat, stirring occasionally. Stir in the parsley about 5 minutes before serving.
    \item Spoon the polenta into warmed shallow bowls and make a well in the center of each serving. Spoon the tomato sauce into the well. Garnish with Parmesan cheese.
\end{enumerate}

\subsection{Substitution Note}
This dish is best made with a rich, creamy bean. If borlotti are unavailable, try French horticulture, or wren's egg.
