\section{Veggie Fried Rice}\index{grains!rice!fried}

\begin{center}
Prep. Time: 5 minutes |
Total Time: 10 minutes
Total Time: 15 min

\noindent Yield: 4 servings

\vspace{1em}

  Source: Lisa Lin (https://healthynibblesandbits.com/easiest-egg-fried-rice/)
\end{center}

\subsection{Ingredients}
\begin{multicols}{2}
\begin{itemize}
    \item 4 large eggs, divided
    \item 2 tablespoons olive oil or canola, divided\footnote{You can also use canola oil, vegetable oil, or peanut oil for this recipe. Peanut oil will give the fried rice a nice light fragrance. I know that olive oil is not traditionally used in Chinese cooking, but in this recipe, you can’t really detect the flavor of the olive oil.}
    \item 1 cup diced red onion (about 1 small onion)\footnote{I used red onion mainly for color. You can use yellow or white onions instead.}
    \item 1 1/3 cups frozen mixed vegetables, thawed
    \item 3 stalks of scallions, sliced
    \item 4 cups cooked brown jasmine rice\footnote{Use day-old rice if possible. Otherwise, try to let the rice cool completely before stir frying. I love the nutty flavor that toasted sesame oil adds to dishes, which is why I included it in the recipe.  Not everyone likes sesame oil. My sister certainly doesn’t. You can still make a tasty fried rice without the sesame oil, so feel free to omit it.}
    \item 2 tablespoons soy sauce (use tamari if gluten free)
    \item 1 teaspoon toasted sesame oil (optional)
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
    \item Crack 3 eggs into a small bowl and beat them together. Beat the last egg in a separate bowl.
    \item Heat a large sauté pan or a wok with 1/2 tablespoon of the olive oil over medium-high heat. Once the pan is hot, add the 3 beaten eggs and scramble them for about a minute. Transfer the eggs to a dish and turn off the heat. Wipe off the pan or wok with a kitchen towel.
    \item Drizzle the remaining 1 1/2 tablespoons of oil in the pan or wok over medium-high heat. Add the onions and cook them for about 2 minutes, stirring constantly. Add the mixed vegetables and scallions and cook for another minute. I like to save some of the scallions (the dark green part) for garnish.
    \item Add the cooked rice into the pan or wok and cook for a few minutes, until the rice is heated through. If you have large clumps of rice, break them apart with the back of your spatula. Pour the single beaten egg over the rice and stir to coat the rice with the egg. Cook for another minute.
    \item Add the soy sauce and sesame oil (if using) and stir to distribute the sauces. Add the 3 scrambled eggs and stir to mix again. Serve immediately.
\end{enumerate}

\subsection{Nutrition Information}
Amount per serving: Calories: 404, Total Fat 14.5g, Saturated Fat: 3g, Cholesterol: 186mg, Sodium: 530mg, Total Carbohydrate: 55.2g, Dietary Fiber: 5.8g, Sugar: 2.2g, Protein 13g

