\section{Fried Zucchini}\index{vegetables!zucchini!fried}

Source: Giada De Laurentiis (http://www.foodnetwork.com/recipes/giada-de-laurentiis/fried-zucchini-recipe/index.html)

\begin{center}
Prep. Time: 15 minutes |
Total Time: 25 minutes | 
Yield: 4 servings
\end{center}

\subsection{Ingredients}
\begin{multicols}{2}
\begin{itemize}
    \item Olive oil, for frying
    \item 1 3/4 cups freshly grated Parmesan
    \item 1 1/2 cups panko (Japanese breadcrumbs)
    \item 3/4 teaspoon salt
    \item 2 large eggs
    \item 3 medium zucchini, cut into 3-inch long by 1/2-inch wide strips
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
    \item Pour enough oil into a large frying pan to reach a depth of 2 inches. Heat the oil over medium heat until a deep-fry thermometer registers 350 degrees F.
    \item Stir 1 1/2 cups Parmesan, the panko, and salt in a medium bowl to blend.
    \item Whisk the eggs in another medium bowl to blend. 
    \item Working in batches, dip the zucchini in the eggs to coat completely and allow the excess egg to drip back into the bowl. Coat the zucchini in the panko mixture, patting to adhere and coat completely. Place the zucchini strips on a baking sheet.
    \item When the oil is hot, working in batches, fry the zucchini sticks until they are golden brown, about 3 minutes.
    \item Using a slotted spoon, transfer the fried zucchini to paper towels and drain.
    \item Arrange the fried zucchini on a platter. Sprinkle with the remaining Parmesan and serve.
\end{enumerate}
