\section{Lentil and Goat Cheese Casserole}\index{vegetables!lentil and goat cheese casserole}

\begin{center}
Total Time: 30 min

\noindent Yield: 2-4 servings

\vspace{1em}

Source: http://greatist.com/eat/recipes/lentil-and-goat-cheese-casserole
\end{center}

\subsection{Ingredients}
\begin{multicols}{2}
\begin{itemize}
    \item 1 cup lentils
    \item 2 cups water
    \item 1/2 tablespoon olive oil
    \item 1/2 red onion, finely chopped
    \item 1 large carrot, grated
    \item 1 clove garlic, finely chopped
    \item Handful fresh parsley, chopped, plus more for garnish
    \item 2 tablespoons chickpea flour
    \item 1 tablespoon soy sauce
    \item Salt
    \item Pepper
    \item Cooking spray
    \item 1/4 cup crumbled goat cheese
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
    \item Preheat oven to 400 degrees.
    \item In a pot ove high heat, bring lentils and water to a boil. Reduce heat to a simmer and let cook until all the water is absorbed. Set aside in a large bowl.
    \item Meanwhile, heat oil in a medium frying pan over medium-high heat. Add onion, carrot, and garlic, and sauté until onion is translucent and other vegetables are tender.
    \item Add cooked vegetables to lentils with parsley, chickpea flour, soy sauce, and salt and pepper to taste. Stir until evenly combined.
    \item Lightly grease a small casserole dish (8-by-8 inch should work) with cooking spray or olive oil, and spread mixture evenly in dish. Top with crumbled goat cheese. Bake casserole for about 10 minutes, or until cheese has softened and melted. Top with additional fresh parsley.
\end{enumerate}

