\section{Lentil Sloppy Joes}\index{vegetables!lentils!lentil sloppy joes}

\begin{center}
Prep Time: 10 min |
Cook Time: 1 hr |
Total Time: 1 hr 10 min

\noindent Yield: 6 servings

\vspace{1em}

Source: http://www.foodnetwork.com/recipes/food-network-kitchens/lentil-sloppy-joes-recipe.html
\end{center}

\subsection{Ingredients}
\begin{multicols}{2}
\begin{itemize}
    \item 2 tablespoons vegetable oil
    \item 1/2 small onion, finely chopped
    \item 1 small carrot, finely chopped
    \item 1/2 bell pepper (red or green), finely chopped
    \item 1/2 cup ketchup
    \item 1 clove garlic, finely chopped
    \item 1/2 cup dried brown lentils, picked over and rinsed
    \item 1/4 teaspoon dried oregano
    \item Kosher salt and freshly ground pepper
    \item 8 ounces ground beef
    \item 1 tablespoon Worcestershire sauce
    \item 6 whole-wheat hamburger buns, toasted
    \item 6 slices cheddar cheese
    \item Sliced pickles and/or pickled jalapeno peppers, for topping (optional)
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
    \item Heat 1 tablespoon vegetable oil in a medium saucepan over medium-high heat. Add the onion, carrot, bell pepper and 2 tablespoons ketchup and cook, stirring occasionally, until the vegetables are slightly soft, about 3 minutes. Add the garlic and cook, stirring, 30 seconds. Add the lentils, oregano and 4 cups water; bring to a boil and cook 5 minutes, then reduce the heat to medium low and simmer until the lentils are tender and the water is absorbed, 35 to 40 minutes (add up to 1 more cup water if necessary). Season with salt and pepper.
    \item Heat the remaining 1 tablespoon vegetable oil in a large nonstick skillet over medium-high heat. Add the beef and cook, breaking it up with a spoon, until it begins to brown, about 2 minutes. Add the Worcestershire sauce and the remaining 6 tablespoons ketchup and cook, stirring, until combined. Add the lentil mixture and 1 cup water and cook, stirring occasionally, until the lentils are soft and the mixture thickens, about 8 minutes. Season with salt and pepper.
    \item Fill the buns with the cheese and lentil mixture. Top with pickles and/or pickled jalapenos.
\end{enumerate}
