\section{Portobello Mushroom, Green Onion and Broccolini Stir-fry}\index{vegetables!broccolini}\index{vegetables!mushrooms!portobello}\index{vegetables!green onions}

Source: adapted from Curtis Stone (http://www.splendidtable.org/recipes/portobello-mushroom-green-onion-and-broccolini-stir-fry)

\begin{center}
Prep. Time: 2 minutes |
Total Time: 2 minutes | 
Yield: 1 Cocktail
\end{center}

\subsubsection{Description}

Portobello mushrooms have a meaty quality that makes them a healthy stand-in for the steak that you might expect to find in this kind of Chinese-style stir-fry. (But you can add some sliced steak, if you wish.) Broccolini is great for stir-frying because its thin stalks cook quickly. Don't confuse it with broccoli rabe, which it resembles -broccolini is much milder. This stir-fry also gets a non-Asian seasoning of thyme, which works beautifully with the other flavors.

\subsection{Ingredients}
\begin{itemize}
    \item 1/4 cup finely chopped shallots
    \item 1/4 cup unseasoned rice vinegar
    \item 2 tablespoons oyster sauce*
    \item 2 teaspoons finely chopped fresh thyme
    \item 3 tablespoons olive oil
    \item 10 ounces broccolini,thick bottoms trimmed, large stalks halved lengthwise**
    \item 2 large portobello mushroom caps, dark gills scraped out with a spoon, cut into 1/2-inch­ thick slices
    \item 6 scallions (white and green parts),cut into 1/2-inch lengths
    \item 1 tablespoon finely chopped peeled fresh ginger
    \item 3 garlic cloves, finely chopped
    \item 1/2 teaspoons sesame seeds,toasted (see below)
    \item Rice, for serving
\end{itemize}

\subsection{Preparation}
\begin{enumerate}
    \item In a small bowl, whisk the shallots, vinegar, oyster sauce,thyme, and 2 table­spoons of the olive oil together.
    \item Heat a wok or large skillet over high heat until very hot. Add the remaining 1 tablespoon olive oil and swirl it to coat the cooking surface with olive oil.
    \item Add the broccolini and cook, stirring often, for about 2 minutes, or until it is bright green and beginning to char in spots. Stir in the mushrooms and cook, stirring often, for about 1 minute, or until they just begin to soften.
    \item Stir in the scallions, ginger, and garlic, add the shallot mixture, and stir for about 3 min­utes, or until the broccolini is tender.
    \item Stir in half of the sesame seeds.
    \item Transfer to a large platter and sprinkle with the remaining sesame seeds. Serve immediately, with the rice.
\end{enumerate}

\subsubsection{Notes}
\textbf{Toasting Seeds}: It only takes a minute or two to toast seeds, and this easy step brings their oils to the surface and really pumps up their flavor. Heat a dry small skillet or wok over medium-high heat. Add the seeds and cook, stirring almost constantly, for about 1 minute (a little longer for pumpkin seeds), or until lightly toasted and fragrant. Transfer to a plate to cool.

\noindent *Omit the oyster sauce and substitute soy sauce for a vegetarian/vegan version of this dish.\\
\noindent **Substitute an equal weight of broccoli florets if broccolini is unavailable
