\section{Refried Black Beans}\index{beans!refried black beans}

\begin{center}
Prep. Time: 5 minutes |
Total Time: 15 minutes
Total Time: 20 min

  \noindent Yield: 4 servings (about 3-4 burritos worth)

\vspace{1em}

  Source: https://www.acouplecooks.com/supremely-simple-refried-black-beans/
\end{center}

\subsection{Ingredients}
\begin{multicols}{2}
\begin{itemize}
  \item 2 garlic cloves
  \item 2 15-ounce cans black beans (or 3 cups cooked black beans)
  \item 2 tablespoons olive oil
  \item 1/2 teaspoon kosher salt
  \item Black pepper
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
  \item Mince the garlic. Drain the beans and reserve the can liquid in a glass measuring cup. (Use water if using cooked beans.)
  \item In a medium saucepan, heat the olive oil over medium heat. Add the garlic and sauté for 1 minute until fragrant but before it browns. Add the beans, 1/2 cup of the reserved can liquid, the kosher salt, and several grinds of black pepper.
  \item Turn the heat to medium low and cook for 10 to 15 minutes, stirring often and smashing the beans toward the end of the cook time, until most of the liquid has cooked out and the texture is mashed and thick, but not dry. Continue to add small amounts of the can liquid if the beans become too dry, and scrape the bottom and sides of the pan until you achieve a fairly creamy consistency where there are still some beans that are whole. Taste and season with additional salt as desired, then serve immediately.
\end{enumerate}
This makes an excellent filling for black bean burritos.
Saut\'{e} up some peppers and onions, mix burrito or taco seasoning with the beans, and put cheese, beans, and veggies in a tortilla.

\subsection{Nutrition Information}
Unknown

