\section{Taco Rice Casserole}\index{grains!rice!taco rice casserole}

\begin{center}
Prep. Time: 5 minutes |
Total Time: 10 minutes
Total Time: 15 min

\noindent Yield: 4 servings

\vspace{1em}

  Source: https://www.eatingonadime.com/taco-rice-casserole-it-freezes-great/
\end{center}

\subsection{Ingredients}
\begin{multicols}{2}
\begin{itemize}
  \item 2 lbs ground turkey (or ground beef)
  \item 1 onion chopped
  \item 1 zucchini shredded (optional)
  \item 2 cups corn
  \item 2 cans black beans
  \item 2 cans diced tomatoes with green chiles (aka Rotel)
  \item 1 package taco seasoning
  \item 4 cups cooked rice
  \item handfuls of shredded cheese
  \item 2 9×13 pans
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
  \item First brown your ground turkey. Add in chopped onions and zucchini (this is optional but ads nutritional value and flavor) and cook until soft.
  \item Stir in Taco seasoning seasoning.
  \item Add corn, tomatoes and beans.
  \item Spray 2 9×13 pans with non stick spray. Spoon 2 cups of rice into the bottom of each pan, spreading it out evenly.
  \item Spoon the meat mixture over the rice.
  \item Top with the shredded cheese.
\end{enumerate}
\textbf{If you want to eat it right away:} Bake covered at 350 degrees for about 25 minutes until cooked through.\\
\textbf{If you want to freeze it:} Cover with foil and label.
To reheat, let thaw overnight in fridge.
Bake at 350 degrees for 45 minutes covered with the foil.
Then remove foil and cook until the top is nice and brown.

\subsection{Nutrition Information}
Amount per serving: Calories: 256, Total Fat 2g, Cholesterol: 41mg, Sodium: 283mg, Potassium: 630mg, Total Carbohydrate: 35, Dietary Fiber: 6g, Sugar: 4g, Protein 24g

