\section{Zucchini Oven Chips}\index{vegetables!zucchini!chips}

Source: Randy Mayor (http://www.health.com/health/recipe/0,,10000001087041,00.html)

\begin{center}
Prep. Time: 2 minutes |
Total Time: 2 minutes | 
Yield: 1 Cocktail
\end{center}

\subsubsection{Description}
Not all chips have to be unhealthy and fat-laden. Zucchinis are more nutritious
than potatoes, which are usually used for chips. Baking the zucchini cuts back
on fat that is needed for frying.

Breaded, oven-fried zucchini chips taste like they're fried, yet they are baked
and amazingly crispy. These chips make a healthy substitute for French fries or
potato chips.

\subsection{Ingredients}
\begin{itemize}
    \item 1/4 cup dry breadcrumbs
    \item 1/4 cup (1 ounce) grated fresh Parmesan cheese
    \item 1/4 teaspoon seasoned salt
    \item 1/4 teaspoon garlic powder
    \item 1/8 teaspoon freshly ground black pepper
    \item 2 tablespoons fat-free milk
    \item 2 1/2 cups (1/4-inch-thick) slices zucchini (about 2 small)
    \item Cooking spray
\end{itemize}

\subsection{Preparation}
\begin{enumerate}
    \item Preheat oven to 425F.
    \item Combine first 5 ingredients in a medium bowl, stirring with a whisk. Place milk in a shallow bowl.
    \item Dip zucchini slices in milk, and dredge in breadcrumb mixture.
    \item Place coated slices on an ovenproof wire rack coated with cooking spray; place rack on a baking sheet. Bake at 425F for 30 minutes or until browned and crisp.
    \item Serve immediately.
\end{enumerate}

\subsubsection{Nutritional Information}
Calories per serving:	61\\
Calories from fat:	28\%\\
Fat per serving:	1.9g\\
Saturated fat per serving:	1g\\
Monounsaturated fat per serving:	0.5g\\
Polyunsaturated fat per serving:	0.2g\\
Protein per serving:	3.8g\\
Carbohydrates per serving:	7.6g\\
Fiber per serving:	1g\\
Cholesterol per serving:	5mg\\
Iron per serving:	0.6mg\\
Sodium per serving:	231mg\\
Calcium per serving:	87mg
