\section{Kale Pepper Baby Frittata Fingers}\index{baby!kale pepper baby frittata fingers}

\begin{center}
Prep Time: 15 min |
Cook Time: 38 min |
Total Time: 53 min

\noindent Yield: 28 frittata fingers

\vspace{1em}

    Source: Abbey Sharp (\url{https://www.abbeyskitchen.com/wprm_print/153121})
\end{center}

\subsection{Ingredients}
\begin{multicols}{2}
\begin{itemize}
    \item 12 omega 3 enriched eggs
    \item 1 tbsp olive oil plus more for greasing
    \item 1 bell pepper minced
    \item 1/2 onion minced
    \item 2 cloves garlic minced
    \item 1/4 cup shredded aged cheddar
    \item 2 cups baby kale ribs removed and finely shredded
    \item 1/2 tsp cumin
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
    \item Preheat oven to 350 F. Lightly grease a 9'' square baking dish.
    \item To a medium skillet, saute the onion, garlic, and bell peppers until soft, about 5-8 minutes. Add the kale and allow to wilt.
    \item Beat the eggs in a bowl, then add in the vegetables, cumin and cheese.
    \item Transfer to the baking dish and bake for 25-30 minutes or until fully set. If you jiggle the pan it should just slightly wobble. Allow to cool.
    \item Cut the frittata into 7 strips one way, and then once down the middle to yield 14 pieces. Then remove the pieces from the pan and cut them in half lengthwise to yield a total of 28 frittata fingers.
\end{enumerate}

\subsection{Nutrition}
\begin{itemize}
    \item Calories: 36kcal
    \item Carbohydrates: 1g
    \item Protein: 3g
    \item Fat: 2g
    \item Saturated Fat: 1g
    \item Cholesterol: 71mg
    \item Sodium: 40mg
    \item Potassium: 61mg
    \item Fiber: 1g
    \item Sugar: 1g
    \item Vitamin A: 725IU
    \item Vitamin C: 11.4mg
    \item Calcium: 26mg
    \item Iron: 0.5mg
\end{itemize}
