\section{Salmon with Lemon, Capers, and Rosemary}\index{salmon}

\begin{center}
Prep. Time: 20 minutes |
Cook Time: 10 minutes|
Total Time: 30 minutes
 
Yield: 4 servings

\vspace{1em}

Source: Giada De Laurentiis\par
http://www.foodnetwork.com/recipes/giada-de-laurentiis/salmon-with-lemon-capers-and-rosemary-recipe/index.html
\end{center}

\subsection{Ingredients}
\begin{itemize}

    \item 4 (6-ounce) salmon fillets
    \item 1/4 cup extra-virgin olive oil
    \item 1/2 teaspoon salt
    \item 1/2 teaspoon freshly ground black pepper
    \item 1 tablespoon minced fresh rosemary leaves
    \item 8 lemon slices (about 2 lemons)
    \item 1/4 cup lemon juice (about 1 lemon)
    \item 1/2 cup Marsala wine (or white wine)
    \item 4 teaspoons capers
    \item 4 pieces of aluminum foil

\end{itemize}

\subsection{Preparation}
\begin{enumerate}
    \item Brush top and bottom of salmon fillets with olive oil and season with salt, pepper, and rosemary.
    \item Place each piece of seasoned salmon on a piece of foil large enough to fold over and seal.
    \item Top the each piece of salmon with 2 lemon slices, 1 tablespoon of lemon juice, 2 tablespoons
          of wine, and 1 teaspoon of capers.
    \item Wrap up salmon tightly in the foil packets.
    
    \item Place a grill pan over medium-high heat or preheat a gas or charcoal grill.
    \item Place the foil packets on the hot grill and cook for 10 minutes for a 1-inch thick piece of salmon.
    \item Serve in the foil packets.
\end{enumerate}

\begin{table}%[H]
    \centering
    \begin{tabular}{|ll|c|}
        \hline
        Calories & & 377\\
        \hline
        Total Fat & & 25 g \\
        & Saturated Fat & 4 g\\
        \hline
        Protein & & 34 g\\
        \hline
        Total Carbohydrates & & 2 g\\
        & Sugar & 1 g\\
        & Fiber & 0 g\\
        \hline
        Cholesterol & & 94 g\\
        \hline
        Sodium & & 451 mg\\
        \hline
    \end{tabular}
    \caption{Nutrition Information for Salmon with Lemon, Capers, and Rosemary}
\end{table}
