\section{Salmon with Mustard and Brown Sugar Glaze}\index{salmon}

Source: http://www.epicurious.com/recipes/food/views/Salmon-with-Mustard-and-Brown-Sugar-Glaze-234419

\begin{center}
Prep. Time: 2 minutes |
Total Time: 2 minutes | 
Yield: 1 Cocktail

\vspace{1em}

Selma Hurwitz of Potomac, Maryland, writes: ``I'm an artist, which helps explain why I think cooking is very creative. You can't be afraid to experiment in the kitchen. I often get ideas from cookbooks and recipes from friends, and I'll add my own touches. The salmon recipe here is based on one a friend gave me. I added more wine, and sometimes I use capers to give the sauce a zesty tang.''
\end{center}

\subsection{Ingredients}
\begin{itemize}
    \item 3/4 cup dry white wine
    \item 1/4 cup butter, cut into small pieces
    \item 1 teaspoon Old Bay seasoning
    \item 1 2-pound center-cut skinless salmon fillet
    \item 1/3 cup spicy brown mustard (such as Gulden's)
    \item 1/4 cup (packed) golden brown sugar
\end{itemize}

\subsection{Preparation}
\begin{enumerate}
    \item Preheat oven to 350°F.
    \item Boil wine, butter, and Old Bay seasoning in small saucepan 3 minutes.
    \item Sprinkle salmon on both sides with salt and pepper. Place fish on heavy rimmed baking sheet. Pour wine mixture over.
    \item Bake until fish is opaque in center, about 14 minutes. Remove from oven.
    \item Preheat broiler.
    \item Mix mustard and sugar in small bowl to blend; spread over salmon to cover.
    \item Broil salmon until topping is brown and bubbling, about 3 minutes.
    \item Transfer salmon to platter and serve.
\end{enumerate}


\subsubsection{Notes}
Broiling caramelizes the sugar and gives the salmon a deeper flavor.



