\section{Shrimp and Pasta in Tomato Chile-Cream Sauce}\index{seafood!shrimp!tomato chile-cream}

Source: http://www.afarmgirlsdabbles.com/2011/02/14/shrimp-and-pasta-in-tomato-chile-cream-sauce/

\begin{center}
Yield: 6 servings
\end{center}

\subsection{Ingredients}
\begin{multicols}{2}
\begin{itemize}
    \item 1/2 tsp. kosher salt
    \item 1 lb. linguine
    \item 2 T. unsalted butter
    \item 2 T. olive oil, divided
    \item 1 lb. large shrimp, peeled and deveined
    \item 2 T. Emeril's Essence Creole*
    \item 1-1/2 tsp. kosher salt, divided
    \item 1 c. finely chopped yellow onion
    \item 1/4 c. finely chopped jalapenos, seeds removed
    \item 1 T. minced garlic
    \item 1-1/2 c. heavy cream
    \item 1/2 tsp. freshly ground black pepper
    \item 1 c. diced tomatoes
    \item 1/2 c. reserved pasta cooking water
    \item 1 c. grated Pepper Jack cheese
    \item 1/4 c. grated Parmesan
    \item 2 T. chopped fresh parsley leaves
    \item 2 T. chopped fresh basil leaves
\end{itemize}
\end{multicols}

* for Emeril's Essence Creole Seasoning, check index

\subsection{Preparation}
\begin{enumerate}
    \item Set a large 1-gallon stock pot of water to a boil.
    \item Add the kosher salt and then the linguine to the pot. Return to a boil and stir the noodles to separate.
    \item Cook the pasta until al dente, about 10 to 12 minutes.
    \item Reserve 1/2 cup of the pasta water and set aside. Drain the pasta.
    \item While the pasta is cooking, start preparing the shrimp and sauce. Set a large deep saute pan over medium-high heat. 
    \item Add the butter and 1 tablespoon of the olive oil.
    \item Once the butter has melted, season the shrimp with 1 tablespoon of the Essence seasoning, plus 1/4 teaspoon of the salt.
    \item Add the shrimp to the pan and sear until nicely browned on both sides. This should take just a couple minutes. Remove the shrimp from the pan and set aside.
    \item Turn heat down to medium and add the remaining tablespoon of olive oil.
    \item Once the oil is shimmering, add the onions and jalapenos to the pan and saut\'{e} until the onions are softened, translucent, and slightly caramelized. This should take about 4 or 5 minutes.
    \item Add the garlic to the pan and saute for 1 minute.
    \item Add the cream, remaining 1 tablespoon of Essence seasoning, remaining 1-1/4 teaspoons of the salt, and the pepper to the pan and bring to a boil.
    \item Cook the sauce until the cream is reduced by half. This should take about 2 minutes.
    \item Return the shrimp to the pan.
    \item Add the linguine, tomatoes, and the reserved cooking water to the pan and cook, tossing to incorporate for 3 to 5 minutes.
    \item Remove pan from the heat and add the Pepper Jack, Parmesan, parsley, and basil.
    \item Toss to blend. Serve immediately.
\end{enumerate}


Servings:  6
