\section{Angel Hair Pasta with Shrimp and Lemon Cream Sauce Recipe}\index{seafood!shrimp!lemon cream sauce}

Source: http://www.simplyrecipes.com/recipes/angel\_hair\_pasta\_with\_shrimp\_and\_lemon\_cream\_sauce

\begin{center}
Prep. Time: 15 minutes |
Total Time: 30 minutes
\end{center}

\subsection{Ingredients}
\begin{itemize}
    \item 3/4 cup heavy whipping cream
    \item 1/4 cup chicken stock
    \item 3 Tbsp lemon juice
    \item 3/4 pound angel hair pasta (also called capellini)
    \item Salt and black pepper
    \item 1 pound raw medium shrimp, peeled and deveined*
    \item 1/2 cup (loosely packed) chopped parsley
    \item 1/4 cup (loosely packed) chopped chives
    \item Zest of a lemon
    \item 1/2 cup freshly grated parmesan cheese
\end{itemize}

\subsection{Preparation}
\begin{enumerate}
    \item Bring a large pot of salted water to a boil.
    \item In a smaller pot, heat the cream, chicken stock and lemon juice to a low simmer. Simmer gently for 5 minutes.
    \item Add the angel hair pasta to the boiling water.
    \item Add the shrimp to the simmering lemon cream sauce. 
    \item Stir well and add a pinch of salt and black pepper. The shrimp should cook in about the same time as the angel hair pasta, about 4 to 5 minutes.
    \item When the pasta is done, drain and put it in a large bowl. Add the herbs to the simmering lemon cream sauce and let them cook for about 1 minute. Pour the shrimp and lemon sauce into the pasta bowl and mix well. Add the lemon zest and most of the parmesan and mix again.
    \item Divide into servings, and top with the remaining parmesan.
\end{enumerate}

Note, if the resulting mixture seems to dry, just add a little water or cream. If it seems to wet, don't worry, the pasta will absorb the sauce.

\subsubsection{Notes}
We used medium shrimp (41-50 per pound) for this recipe, but little cocktail shrimp would also work. Use heavy whipping cream to avoid curdling when mixed and heated with the lemon juice.

\noindent *To defrost frozen shrimp, place them in a bowl of ice water.
