\section{Shrimp Mozambique}\index{seafood!shrimp!mozambique}

Source: shermcr on Epicurious | Updated: December 21, 2008

\begin{center}
Prep. Time: 20 minutes |
Total Time: 30 minutes
\end{center}

\subsubsection{Description}
Despite the African sounding name, this is actually a Portuguese dish. The real recipe calls for saffron, but sazon goya con azafran makes a great substitute. Perhaps this dish's best feature is that in addition to being delicious, it's really quick and easy!

Read More http://www.epicurious.com/recipes/food/printerfriendly/SHRIMP-MOZAMBIQUE-50012773\#ixzz2SYqaD4Pd

\subsection{Ingredients}
\begin{multicols}{2}
\begin{itemize}
    \item 12 - 14 shrimp (med/lrg)
    \item 1 medium onion chopped fine
    \item 1.5 tblsp parsley
    \item 1 packet ``sazon goya con azafran''
    \item 1/2 tsp salt
    \item 1/2 tsp white pepper
    \item 1/2 tsp crushed red pepper
    \item 3 cloves garlic
    \item 2 tblsp butter
    \item 1 tblsp olive oil
    \item 1/2 - 3/4 cup white wine or beer
    \item 1 to 1-1/2 cups white rice
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
    \item In a small mixing bowl add garlic, sazon goya, crushed red pepper, salt and pepper. Mix gently.
    \item Add 1.5 tblsp butter and olive oil to pan with onion and cook until soft, 4-5 mintues over medium heat.
    \item Add contents of mixing bowl, stir, and cook for 1-2 minutes.
    \item Add wine/beer, bring to boil and reduce for 2 minutes over medium high heat.
    \item Add shrimp, parsley and rest of butter.
    \item Cook over medium heat until shrimp are done and serve over rice. Super easy and quick.
\end{enumerate}
