\section{Shrimp Scampi}\index{seafood!shrimp!scampi}

Source: http://www.simplyrecipes.com/recipes/shrimp\_scampi/

\begin{center}
Prep. Time: 10 minutes |
Total Time: 15 minutes |
Yield: 4 servings
\end{center}

\subsection{Ingredients}
If you are using frozen shrimp, defrost them quickly and safely by putting the shrimp in a large bowl of ice water.
\begin{multicols}{2}
\begin{itemize}
    \item 1 pound large (16-20 count) shrimp, shelled* and de-veined, tail-on for presentation if you want
    \item Salt
    \item 3-4 garlic cloves, slivered, or 1 Tbsp minced garlic
    \item 2 tablespoons olive oil
    \item 2-3 tablespoons butter
    \item 2 tablespoons finely chopped parsley
    \item 1/2 cup white wine
    \item 1/2 to 1 teaspoon red pepper flakes
    \item Freshly ground black pepper to taste
    \item 1 Tbsp lemon juice
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
    \item Heat a saut\'e pan on high heat. Reduce the heat to medium-high and add the olive oil and butter.
    \item Once the butter melts, foams up and subsides, add the garlic and red pepper flakes. Saut\'e for a minute, or until you see the edges of some of the garlic just beginning to brown.
    \item As soon as the garlic begins to brown, add the shrimp to the pan. Then add the white wine and stir to combine and coat the shrimp with the butter, oil, and wine.
    \item Spread the shrimp out in an even layer in the pan. Increase the heat to the highest setting and let the wine boil vigorously for 2-3 minutes.
    \item Turn the shrimp over, or toss them so the cooked sides are mostly facing up, and boil the wine for another minute.
    \item Remove from the heat, add the parsley and toss to combine. Add the lemon juice and black pepper.  
    \item Serve alone, with crusty bread, over pasta, or over rice (for gluten-free 
version).
\end{enumerate}

\subsubsection{Notes}
* Whether you prepare the shrimp shell on or off is really up to you. Cooking 
  the shrimp with the shells still on will impart more flavor, but they are much
  messier to eat. Shelling the shrimp before cooking them will make the shrimp a
  lot easier to eat and you can save the shells for shellfish stock if you want.
