\section{Sweet and Spicy Baked Shrimp Tacos}\index{seafood!shrimp!sweet and spicy tacos}

\begin{center}
Prep. Time: 15 minutes |
Cook Time: 5 minutes|
Total Time: 20 minutes
 
Yield: 8 tacos

\vspace{1em}

Source: Land-O-Lakes butter carton\par

\vspace{1em}
Spice-coated shrimp are backed and then placed on top of corn tortillas.
Add coleslaw mix and drizzle with a flavorful sauce for a new twist on tacos.

\end{center}

\subsection{Ingredients}
\textbf{Spice Mixture}
\begin{multicols}{2}
\begin{itemize}
    \item 1/3 cup sugar
    \item 3 tbsp firmly packed brown sugar
    \item 2 tbsp all-purpose flour
    \item 2 tbsp plain breadcrumbs
    \item 1/2 tsp ground allspice
    \item 1/2 tsp coarse ground black pepper
    \item 1/2 tsp ground red pepper
    \item 1/4 tsp garlic powder
    \item 1/4 tsp ground ginger
\end{itemize}
\end{multicols}

\noindent\textbf{Shrimp}
\begin{itemize}
    \item 1/4 cup unsalted butter, melted
    \item 1 lb uncooked, thawed, medium shrimp
\end{itemize}

\noindent\textbf{Sauce}
\begin{itemize}
    \item 1/2 cup sour cream
    \item 1 tbsp lime juice
    \item 2 tsp chopped fresh cilantro
    \item 1/2 chili powder
\end{itemize}

\noindent\textbf{Tacos}
\begin{itemize}
    \item 16 6-inch corn tortillas, warmed
    \item 2 cups coleslaw mix
\end{itemize}

\subsection{Preparation}
\begin{enumerate}
    \item Heat oven to 500$^o$F and line backing sheet with aluminum foil; set aside.
    \item Combine all spice mixture ingredients in a small bowl. Dip the shrimp in
          butter then in the spice mixture. Place onto prepared backing sheet. Bake
          for 5 to 6 minutes or until shrimp are pink and coating is bubbly.
    \item Meanwhile, combine all sauce ingredients in a small bowl.
    \item To assemble tacos, stack 2 warmed tortillas onto each individual serving
          plate. Top with 1/8 baked shrimp and 1/4 cup coleslaw mix. Drizzle with sauce.
\end{enumerate}
