\section{Mozzarella Sticks}\index{cheese}

Source: Giada De Laurentiis |
Show: Everyday Italian |
Episode: Burgers and Fries

\subsection{Ingredients}
\begin{multicols}{2}
\begin{itemize}
    \item 1 1/2 cups Italian-style dried breadcrumbs
    \item 1 1/3 cups freshly grated Parmesan
    \item 1 teaspoon salt
    \item 2 (16-ounce) blocks pasteurized mozzarella cut into 4 by 1/2-inch sticks
    \item 4 large eggs, beaten to blend
    \item 1 1/2 cups vegetable oil
    \item 4 cups Marinara Sauce, recipe follows
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
    \item Stir the bread crumbs, 1 cup of Parmesan and 1 teaspoon of salt in a medium bowl to blend. 
    \item Dip the cheese in the eggs to coat completely and allow the excess egg to drip back into the bowl. 
    \item Coat the cheese in the bread crumb mixture, patting to adhere and coat completely. 
    \item Place the cheese sticks on a baking sheet. Repeat dipping the cheese sticks in the egg and bread crumb mixture to coat a second time. 
    \item Cover and freeze until frozen, about 2 hours and up to 2 days.

    \item Heat the oil in a large frying pan over medium heat. 
    \item Working in batches, fry the cheese until golden brown, about 1 minute per side. 
    \item Transfer the fried cheese to plates. 
    \item Sprinkle with the remaining cheese and serve with the Marinara Sauce.
\end{enumerate}

\section{Marinara Sauce}\index{sauces!marinara}

\noindent Prep. Time: 10 minutes |
Total Time: 1 hour 10 minutes | 
Yield: 2 quarts

\subsection{Ingredients}
\begin{multicols}{2}
\begin{itemize}
    \item 1/2 cup extra-virgin olive oil
    \item 2 small onions, finely chopped
    \item 2 garlic cloves, finely chopped
    \item 2 stalks celery, finely chopped
    \item 2 carrots, peeled and finely chopped
    \item 1/2 teaspoon sea salt, plus more to taste
    \item 1/2 teaspoon freshly ground black pepper, plus more to taste
    \item 2 (32 ounce) cans crushed tomatoes
    \item 2 dried bay leaves
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
    \item In a large casserole pot, heat the oil over a medium-high flame.
    \item Add the onions and garlic and saute until the onions are translucent, about 10 minutes. 
    \item Add the celery, carrots, and 1/2 teaspoon of each salt and pepper. Saute until all the vegetables are soft, about 10 minutes. 
    \item Add the tomatoes and bay leaves, and simmer uncovered over low heat until the sauce thickens, about 1 hour.
    \item Remove and discard the bay leaf. Season the sauce with more salt and pepper, to taste. (The sauce can be made 1 day ahead. Cool, then cover and refrigerate. Rewarm over medium heat before using.)
\end{enumerate}
