\section{Greek Tzatziki Sauce Recipe}\index{condiments!stacey's hamburger seasoning}

\begin{center}
Total Time: 15 min

\noindent Yield: 3 cups

\vspace{1em}

    Source: Suzy (\url{https://www.themediterraneandish.com/tzatziki-sauce-recipe/})

    Creamy Greek Tztaziki Sauce.
    A versitle Greek yogurt and cucumber sauce to serve along with veggies and pita, spread on sandwiches, or add it next to grilled fish, meat or poultry!
\end{center}

\subsection{Ingredients}
\begin{multicols}{2}
\begin{itemize}
    \item 3/4 English cucumber, partially peeled (striped) and sliced
    \item 1 tsp kosher salt, divided
    \item 4 to 5 garlic cloves, peeled, finely grated or minced (you can use less if you prefer)
    \item 1 tsp white vinegar
    \item 1 tbsp Early Harvest  Greek Extra Virgin Olive Oil
    \item 2 cups Greek yogurt (I used organic fat free Greek yogurt, but you can use 2% or whole milk Greek yogurt, if you like)
    \item 1/4 tsp ground white pepper
    \item Warm pita bread for serving
    \item Sliced vegetables for serving
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
    \item Prep the cucumber. In a food processor, grate the cucumbers. Toss with 1/2 tsp kosher salt. Transfer to a fine mesh strainer over a deep bowl to drain. Spoon the grated cucumber into a cheese cloth or a double thickness napkin and squeeze dry. Set aside briefly.
    \item In one large mixing bowl, place the garlic with remaining 1/2 tsp salt, white vinegar, and extra virgin olive oil. Mix to combine.
    \item Add the grated cucumber to the large bowl with the garlic mixture. Stir in the yogurt and white pepper. Combine thoroughly. Cover tightly and refrigerate for a couple of hours.
    \item When ready to serve, stir the tzatziki sauce to refresh and transfer to serving bowl, drizzle with more extra virgin olive oil, if you like. Add a side of warm pita bread and your favorite vegetables. (also see notes for more ideas) Enjoy!
\end{enumerate}

\subsection{Notes}
\begin{enumerate}
    \item This recipe is adapted from \href{https://www.amazon.com/Yogurt-Culture-Global-Creamiest-Healthiest/dp/0544252322}{Yogurt Culture}.
        It is my quick version, and it's been cut down to suit a smaller family.
    \item Cook's Tips: This is very garlicky dip, if you prefer, start with a smaller amount of garlic and incorporate more as needed. And to change things up, feel free to stir in a tablespoon or so of chopped fresh dill or fresh mint.
    \item To Store: It's best to store tzatziki in the fridge in a tightly-covered glass container, and use within 2 to 4 days.
    \item Suggestions for Use: Tzatziki makes the perfect topping for \href{https://www.themediterraneandish.com/mediterranean-loaded-baked-potato-recipe/}{Mediterranean-style baked potato}; or next to \href{https://www.themediterraneandish.com/mediterranean-whole-roasted-red-snapper-recipe-with-garlic-and-vegetables/}{stuffed snapper} or \href{https://www.themediterraneandish.com/mediterranean-seared-trout-recipe-tzatziki/}{pan-seared trout}; \href{http://www.themediterraneandish.com/mediterranean-grilled-lamb-chop-recipe-with-tomato-mint-quinoa/}{lamb chops}; \href{https://www.themediterraneandish.com/greek-chicken-souvlaki-recipe-tzatziki/}{chicken souvlaki}; \href{http://www.themediterraneandish.com/chicken-shawarma-sliders/}{shawarma} and more! I also use it simply as a sandwich spread.
\end{enumerate}

