\section{Simple Syrup}\index{syrup!simple}\index{sugar!simple syrup}

Prep. Time: 5 minutes |
Total Time: 5 minutes

\subsection{Ingredients}
\begin{itemize}
    \item 2 parts sugar
    \item 1 part water
\end{itemize}

\subsection{Preparation}
\begin{enumerate}
    \item Bring the water to a boil.
    \item Dissolve the sugar into the boiling water, stirring constantly.
    \item Once the sugar is dissolved completely, remove the pan from the heat. (Note: Do not allow the syrup to boil for too long or the syrup will be too thick.)
    \item Allow to cool completely and thicken, then bottle.
\end{enumerate}

To prolong the shelf life of your simple syrup, add a little vodka - usually between a tablespoon and an ounce, depending on how large the batch of syrup is.

\subsection{Variations}

\subsubsection{Demerara Syrup}\index{sugar!turbinado}
Replacing white sugar with Demerara sugar (a raw sugar) is a popular alternative because it has a richer sugar flavor. The drawback to using this light brown sugar is that it will alter the color of cocktails and while the difference is noticeable, the taste makes up for it. Another option is to use turbinado or brown sugars.

\subsubsection{Bar Simple Syrup}
The easiest way to make simple syrup does not require a stove and can be made in minutes. Simply combine equal parts (1:1) sugar and water in a bottle and shake it until the sugar is completely dissolved. The result is a syrup that is thinner than rich simple syrup.

\subsubsection{Flavor-infused simple syrups}
Simple syrup can also be infused with flavor and used in a variety of cocktails to add a unique twist.
