\section{Chicken Enchiladas}\index{poultry!chicken!chicken enchiladas}

\begin{center}
Prep Time: 15 min |
Cook Time: 45 min |
Total Time: 1 hour

\noindent Yield: 6-8 servings

\vspace{1em}

Source: http://www.gimmesomeoven.com/best-chicken-enchiladas-ever/
\end{center}

\subsection{Ingredients}
\begin{multicols}{2}
\begin{itemize}
    \item 2 Tablespoons vegetable oil
    \item 1 small white onion, peeled and diced
    \item 1.5 pounds boneless skinless chicken breasts, diced into small 1/2-inch pieces (*or see substitution below for using pre-cooked shredded chicken) salt and pepper
    \item 1 (4-ounce) can diced green chiles
    \item 1 (15.5 ounce) can black beans or lentils, rinsed and drained
    \item 8 large flour tortillas
    \item 3 cups Mexican-blend shredded cheese
    \item 1 batch red enchilada sauce, or 1 can store-bought enchilada sauce
    \item (optional: 1/4 cup chopped fresh cilantro)
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
    \item Preheat oven to 350 degrees F.  Prepare your enchilada sauce, if making homemade.
    \item In large skillet, heat oil over medium-high heat. Add onion and saute for 3 minutes, stirring occasionally.  Add diced chicken and green chiles, and season with salt and pepper.  Saut\'{e} for 6-8 minutes, stirring occasionally, or until the chicken is cooked through.  Remove from heat and set aside.
    \item To assemble the enchiladas, set up an assembly line including: tortillas, enchilada sauce, beans, chicken mixture, and cheese. Lay out a tortilla, and spread two tablespoons of sauce over the surface of the tortilla.  Add beans in a line down the middle of the tortilla, then add in a spoonful of the chicken mixture, then sprinkle with 1/3 cup cheese. Roll up tortilla and place in a greased 9 x 13-inch baking dish. Repeat with the remaining ingredients.  Then spread the remaining enchilada sauce on top of the tortillas, and sprinkle on the remaining shredded cheese.
    \item Bake uncovered for 20 minutes.  Remove from oven and serve immediately, garnished with chopped fresh cilantro if desired.
\end{enumerate}
*If you are using pre-cooked chicken, just leave it out of the saute and cook the onion and green chiles for 1 additional minute (instead of 6-8).  Once you remove the onion and green chiles from the heat, stir in the chicken (which should be shredded or chopped into bite-sized pieces).

\subsection{Notes}
Melissa made the following alterations:
\begin{itemize}
    \item Seasoned chicken with fajita seasoning, used chipotle peppers in adobo sauce instead of green chiles
    \item Added bell pepper and onions when cooking chicken
    \item Changed corn to black beans

See next recipe for red enchilada sauce (p. \pageref{red-enchilada-sauce})
\end{itemize}
