\section{Chicken, Peppers, Onions, and Mushrooms with Marsala Wine}\index{poultry!chicken!chicken, peppers, onions, mushrooms and marsala wine}

\begin{center}
Prep Time: 10 min | 
Cook Time: 20 min | 
Total Time: 30 min

\noindent Yield: 4 servings

\vspace{1em}

Source: http://www.myrecipes.com/recipe/chicken-peppers-onions-mushrooms-with-marsala-wine
\end{center}

\subsection{Ingredients}
\begin{multicols}{2}
\begin{itemize}
    \item 1 1/2 pounds chicken breast tenders
    \item 1 1/2 cups thinly sliced onion
    \item 1 cup thinly vertically sliced red bell pepper (about 1 medium)
    \item 2 tablespoons olive oil
    \item 1/2 teaspoon salt
    \item 1/2 teaspoon black pepper
    \item 1 (8-ounce) package presliced exotic mushroom blend (such as shiitake, cremini, and oyster)
    \item 3 tablespoons Marsala wine
\end{itemize}
\end{multicols}

\subsection{Preparation}
\begin{enumerate}
    \item Heat a large nonstick skillet over medium-high heat. Coat pan with cooking spray.
    \item Add chicken breast tenders to pan; sauté 7 minutes or until the chicken is done. Remove chicken from pan.
    \item Add sliced onion and sliced bell pepper to pan; sauté 5 minutes or until onion starts to brown.
    \item Add olive oil, salt, black pepper, and presliced exotic mushrooms to pan; saut\'{e} 3 minutes or until mushrooms are tender and onion starts to caramelize.
    \item Add Marsala wine and chicken to pan, and cook for 1 minute or until thoroughly heated.
    \item Serve immediately.
\end{enumerate}

Calories 295  Caloriesfromfat 28\%  Fat 9.2 g  Satfat 1.6 g  Monofat 5.4 g  Polyfat 1.3 g  Protein 41.8 g  Carbohydrate 8.9 g  Fiber 1.8 g  Cholesterol 99 mg  Iron 1.8 mg  Sodium 411 mg  Calcium 33 mg
